\section{Censorship of IPv4 and IPv6 Resource Records} \label{sec:resources}

\para{Overview.}
In this section, we focus on {\it identifying and characterizing differences in
the handling of IPv4 and IPv6 resource records} in DNS censorship deployments.
Specifically, we seek to answer the following questions: 
%
(\Cref{sec:resources:country}) In which countries is the censorship of IPv4
\textbf{resource records} (DNS {\tt A} queries) significantly different than the
censorship of IPv6 resource records (DNS {\tt AAAA} queries)?,
%
(\Cref{sec:resources:resolvers}) what are the characteristics of the \textbf{resolvers}
which exhibit differences in the handling of {\tt A} and {\tt AAAA} queries?,
and 
%
(\Cref{sec:resources:domains}) what are the characteristics of \textbf{domains} in which
these differences are frequently observed?
%

%\subsection{Within-country differences in the censorship of
%\texttt{A} and \texttt{AAAA} resource records} \label{sec:resources:country}
\subsection{{\tt A} vs. {\tt AAAA} resource censorship} \label{sec:resources:country}
%
We use the responses received from our {\tt A} and {\tt AAAA} queries sent to
the same set of resolvers and for the same set of domains (\cf
\Cref{sec:methods:gathering} for a detailed description of our data gathering
process). We then apply the censorship determination methods described in
\Cref{sec:methods:labeling} to measure the prevalence of censorship on our {\tt
A} and {\tt AAAA} DNS queries. Finally, we perform statistical tests to
identify significant differences in the prevalence of censorship of {\tt A} and
{\tt AAAA} queries within each country.

\para{Identifying differences within a country.}
To measure differences in DNS query handling within a specific country, we
compare the prevalence of censorship on {\tt A} and {\tt AAAA} queries by
aggregating responses across {each resolver within the country}. This presents
us with two distributions (one each for the group of {\tt A} and {\tt AAAA}
queries) of the fraction of censored domains observed at each resolver in the
country.
%
We use a two-sample $t$-test to verify statistical significance of any observed
differences between the two groups for each country. In our statistical
analysis, we aim to achieve a significance level of 5\% ($p \leq$  .05)
\emph{over all our findings}. Therefore, we apply a Sidak correction
\cite{abdi2007bonferroni} to control for Type I (false-positive) errors from multiple hypothesis
testing. 
%
This requires $p \leq 1-{.05}^{1/n_{c}}$ for classifying a difference as
significant, where $n_c$ is the total number of countries in our dataset
(\fixme{XXX}). This approach reduces the likelihood of false-positive reports
of within-country differences.
%
The presence of a statistically significant difference for a specific country
would imply that \texttt{A} and \texttt{AAAA} resource types appear to undergo different censorship
mechanisms within that country (if a centralized mechanism for censorship
exists) or that a significant number of resolvers within that country have
inconsistencies in their censoring of each query type.
%
A summary of our results are presented in \Cref{tab:resources:countries}. 

\para{How many countries demonstrate large-scale inconsistencies in their
handling of {\tt A} and {\tt AAAA} queries?} 
%
In total, only seven countries showed a statistically significant difference
in the rate at which {\tt AAAA} and {\tt A} DNS requests were blocked. We note
that this is a conservative lower-bound due to the statistical test used, which
minimizes false positive errors at the expense of false negatives.
%
This finding suggests the presence of independent censorship mechanisms for
handling each query type in the seven countries (Thailand, Bangladesh,
Pakistan, Chile, Vietnam, Korea, and China).
%
Of these, six (China being the only exception) were found to have lower
blocking rates for {\tt AAAA} queries than {\tt A} queries. In fact, the {\tt
AAAA} censorship rates were between 36-78\% lower than the {\tt A} censorship
rate suggesting that their censorship mechanisms for {\tt AAAA} queries that
are associated with IPv6 connectivity are still lagging. 
%
Further analysis shows that the differences are mostly found on the IPv4
interfaces of our resolvers (\cf {\it IPv4 resolvers} column in
\Cref{tab:resources:countries}) where the {\tt AAAA} censorship rates were up to
86\% lower than the {\tt A} censorship rates. 
%
This finding is indicative of a tendency for network operators to have
focused efforts on maintaining infrastructure for censoring {\tt A} queries
sent to IPv4 resolvers, while paying less attention to the handling of {\tt
AAAA} queries and their IPv6 interfaces. It also presents an opportunity for
circumvention tool developers to exploit.
%
%Once again, 
China presents the only exception with a preference for blocking
{\tt AAAA} queries on both IPv4 and IPv6 interfaces of resolvers with a 10\%
and 13\% higher {\tt AAAA} censorship rate, respectively. We investigate this
anomaly in \Cref{sec:cases}.

\begin{table}[t]
  \centering
  \small
  \scalebox{\tabularscale} {
  \begin{tabular}{lccc}%p{.9in}p{.9in}}
    \toprule
    {\bf Country}&{\bf IPv4 resolvers}&{\bf IPv6 resolvers} & {\bf All resolvers}
    \\ \midrule
    Thailand (TH)      & -7.1 pp (-85.7\%) & $ns$               & -3.7 pp (-77.5\%) \\
    Bangladesh (BD)    & -5.1 pp (-80.0\%) & $ns$               & -2.6 pp (-71.3\%) \\
    Pakistan (PK)      & -2.1 pp (-73.6\%) & -2.8 pp (-59.8\%)  & -2.5 pp (-60.2\%) \\
    Chile (CL)         & -2.0 pp (-57.6\%) & $ns$               & -1.1 pp (-58.9\%) \\
    Vietnam (VN)       & $ns$              & -0.7 pp (-52.5\%)  & -0.7 pp (-47.1\%) \\
    Korea (KR)         & -1.3 pp (-54.6\%) & $ns$               & -0.6 pp (-36.2\%) \\
    China (CN)         &  3.1 pp (+10.4\%) &  3.7 pp (+12.9\%)  &  3.4 pp (+11.7\%) \\
    \midrule
    United States (US) & -0.5 pp (-33.2\%) &  0.4 pp (+72.3\%)  &  $ns$  \\
    Myanmar (MY)       & -2.9 pp (-58.9\%) & $ns$    &  $ns$  \\
    \bottomrule
  \end{tabular}
  }
  \caption{Differences in blocking rates of {\tt A} and {\tt AAAA} queries
  observed over IPv4, IPv6, and all resolvers in a country. `pp' denotes the
  change in terms of percentage points (computed as {\tt AAAA} blocking rate
  - {\tt A} blocking rate) and the \%age value denotes the percentage change in
  blocking rate (computed as
  $
  100\times\frac{\text{{\tt AAAA} blocking rate} - \text{{\tt A} blocking rate}}
  {\text{{\tt A} blocking rate}}
  $). 
  Only countries having
  a statistically significant difference are reported. A negative value
  indicates that {\tt A} queries observed higher blocking rates than {\tt AAAA}
  queries. $ns$ indicates the difference was not statistically significant and
  thus omitted.}
  \label{tab:resources:countries}
\end{table}

\subsection{Characteristics of {\tt A/AAAA}-inconsistent resolvers}
\label{sec:resources:resolvers}
Given our above results which suggest that there are a number of countries in
which {\tt A} and {\tt AAAA} queries are censored differently, we now seek to
understand the characteristics of the resolvers that cause these differences.
%
We first focus on identifying the individual resolvers in each country that
have statistically different behaviors for {\tt A} and {\tt AAAA} queries.
Then, we compare the AS distributions of these resolvers with the set of all
resolvers in a country. This comparison tells us if the {\tt A}/{\tt AAAA}
inconsistencies are specific to a subset of ISPs, or if the inconsistencies
exist across the whole country (suggesting centralized censorship).
Finally, we identify the
types of networks hosting inconsistent resolvers to get a measure of whether
users in residential networks may exploit these DNS inconsistencies for
circumvention.

\para{Identifying differences in individual resolvers.}
%
We begin our analysis by identifying the individual resolver pairs (\ie we
consider the IPv4- and IPv6-interfaces of a resolver as a unit), within each
of the seven countries listed above that have a statistically significant
difference in their censorship of {\tt A} and {\tt AAAA} queries.
%
To measure differences in DNS query handling of individual resolvers, we
compare the ratio of censored responses each resolver observes for {\tt A} and
{\tt AAAA} queries.

%observed from our {\tt A} and {\tt
%AAAA} queries {from each resolver}.
%
We use a two-proportion $z$-test to verify the statistical significance of any
observed difference in the ratios between the two groups for each resolver.
Similar to our within-country analysis, we apply a Sidak correction to account
for our testing of multiple hypotheses and use $p \leq 1-{.05}^{1/n_{r_c}}$ to
classify a difference as significant, where $n_{r_c}$ is the total number of
resolvers in our dataset belonging to country $c$.
%
A summary of our results is provided in \Cref{tab:resources:resolvers}. 

\para{Which countries have the largest fractions of resolvers
exhibiting {\tt A} and {\tt AAAA} resolution inconsistencies?}
%
Immediately standing out from the other countries are Thailand, Bangladesh, and
Pakistan. These countries have {\tt A} and {\tt AAAA} inconsistencies in
62-82\% of their resolvers. In comparison, other countries with
statistically significant differences have inconsistencies arising from
anywhere between 3-30\% of their resolvers.
%

\para{How spread out are the {\tt A/AAAA}-inconsistent resolvers?}
We calculate the entropy of the distribution of all resolvers in the
country ($S_{\text{query}}^{\text{all}}$) and compare it with the entropy of
the distribution of the inconsistent resolvers in the country
($S_{\text{query}}^{\text{inconsistent}}$). This serves as a measure of the
diversity of ASes observed in both cases. 
%
In order to compare the two measures, we use the Kullback-Leibler divergence
($\nabla_{\text{query}}$) distance \cite{KLdivergence}. In simple terms, the
KL-divergence between two distributions ($X$, $Y$) measures the number
of additional bits required to encode $Y$ given the optimal encoding for $X$. In
other words, it is the relative entropy of one distribution given another. 
%If the distributions are similar, the number will be close to 0.
%
This computation is helpful for hypothesizing the censorship infrastructure
that causes the inconsistencies. Finding a small $\nabla_{\text{query}}$ value
in a country signifies that the inconsistent resolvers had a similar
distribution to all the resolvers in that country. This would suggest the
presence of a centralized mechanism that (roughly) equally impacts all ASes in
the country that is responsible for the inconsistencies.
Conversely, a higher $\nabla_{\text{query}}$ value indicates that there is
a strong change in the distribution of resolvers -- \ie a disproportionate
number of inconsistencies arise from a smaller set of ASes. This would be
indicative of local configuration inconsistency (at the network or resolver
level), rather than a centralized configuration inconsistency.
%
We note that this does not provide a measure of how centralized censorship is
within a country overall, but rather, it describes how uniform the {\tt A} vs.
{\tt AAAA} inconsistencies are.

%
Based on this analysis, we once again see that Thailand, Bangladesh, and
Pakistan stand out with small $\nabla_{\text{query}}$ values (0.14 - 0.48).
This suggests a country-wide censorship mechanism is responsible
for the inconsistent censorship of {\tt A} and {\tt AAAA} that impacts all
ASes nearly equally.
%
Korea, China, and the United States on the other hand demonstrate high
$\nabla_{\text{query}}$ scores suggesting the presence of network- or
resolver-level misconfigurations are responsible. This is confirmed by inspecting the ASes
hosting the resolvers with inconsistencies. For example, in the United States,
resolvers in just 5 ASes (of 249 ASes with resolvers) account for 56\% of all
{\tt A} and {\tt AAAA} inconsistencies.


\begin{table*}[t]
  \centering
  \small
  \scalebox{\tabularscale} {
    \begin{tabular}{lcclcccl}
    \toprule
      {\bf Country} & {\bf Total pairs} & {\bf Inconsistent pairs} & {\bf Most inconsistent AS} & \multicolumn{3}{c}{\bf AS diversity} & {\bf Most inconsistent type} \\ 
      & & {(\% of total pairs)}& {(\# inconsistent pairs)} & $S^{\text{all}}_{\text{query}}$ & $S^{\text{inconsistent}}_{\text{query}}$ & $\nabla_{\text{query}}$  & {(\# inconsistent pairs)} \\
      \midrule
      Thailand (TH)       & 186 & 152 (81.7\%)  &  AS9835 Government IT Services (40)  & 4.50 & 4.06 & 0.14 & Cable/DSL (110) \\
      Bangladesh (BD)     & 29  & 18 (62.1\%) & AS 9230 Bangladesh Online (4)          & 4.10 & 3.61 & 0.48 & Cable/DSL (18) \\    
      Pakistan (PK)       & 23  & 15 (65.2\%) & AS 17911 Brain Telecom (3)             & 3.43 & 3.06 & 0.25 & Cable/DSL (12) \\    
      Chile (CL)          & 65  & 20 (30.1\%) & AS 27651 Entel Chile (13)              & 3.08 & 1.14 & 1.18 & Corporate (13) \\    
      Vietnam (VN)        & 252 & 64 (25.4\%) & AS 131353 NhanHoa Software (37)        & 3.89 & 2.22 & 0.71 & Cable/DSL (59) \\    
      Korea (KR)          & 632 & 80 (12.7\%) & AS 9848 Sejong Telecom (13)            & 3.12 & 4.17 & 1.30 & Cable/DSL (58) \\    
      China (CN)          & 194 & 6 (3.1\%)   & AS 4538 China Education and Research Network (2) & 3.89 & 2.25 & 2.56 & Corporate (4)   \\    
    \midrule
      United States (US)  & 1,228 & 175 (14.3\%)  & AS 30475 WEHOSTWEBSITES (35) & 6.28 & 4.69 & 1.31 & Corporate (129) \\    
      Myanmar (MY)        & 50  & 30 (60\%)   & AS 136170 Exabytes Network (10)  & 3.31 & 2.42 & 0.48 & Corporate (26) \\    
    \bottomrule
  \end{tabular}
  }
  \caption{Characteristics of the resolvers which demonstrated a statistically
  significant difference in their handling of {\tt A} and {\tt AAAA} queries in
  each country. 
  %
  `AS diversity' denotes the entropies of (all) resolver distribution
  ($S^{\text{all}}_{\text{query}}$) and {\tt A/AAAA}-inconsistent resolver
  distribution ($S^{\text{inconsistent}}_{\text{query}}$) across a country's
  ASes, and `$\nabla_{\text{query}}$' represents the Kullback-Leibler
  divergence of the distribution of inconsistent resolvers from the
  distribution of all resolvers in the country's ASes (\cf
  \Cref{sec:resources:resolvers}).
  %
  `Most inconsistent type' denotes the connection type with the most number of
  {\tt A/AAAA}-inconsistent resolvers.}
  \label{tab:resources:resolvers}
\end{table*}

\para{What types of networks exhibit the most {\tt A} and {\tt AAAA}
inconsistencies?}
%
We use the Maxmind GeoIP2 connection type database (retrieved in 01/2022
\cite{maxmind-connectiondb}) to identify the connection type of the resolvers
responsible for {\tt A} and {\tt AAAA} inconsistencies. 
%
We find that, in most countries, Cable/DSL network connections (typically
associated with residential networks) were most likely to host a resolver
exhibiting an inconsistency. 
%
Of the seven countries with statistically significant overall differences, only
Thailand and China were found to have a high ratio of {\tt A/AAAA} -inconsistent
resolvers in corporate networks. 
%
Combined with our previous results which suggest the presence of an
inconsistency in a centralized mechanism in Thailand, Bangladesh, and Pakistan,
these results show that these inconsistencies are likely extending to
residential networks --- a promising sign for the citizen users of
circumvention tools which exploit the {\tt A/AAAA} gap.

\subsection{Characteristics of anomalous domains} 
\label{sec:resources:domains}

\para{Identifying differences in domain behaviors within a country.} 
To uncover the domains which have their {\tt A} and {\tt AAAA} queries treated
differently within a country, we compare the ratios of censored responses in
each group for each domain across all resolvers within a country.  
%
We use a two-proportion $z$-test to verify the statistical significance of any
observed differences between the two query types for each domain tested within
each country. We once again apply a Sidak correction to ensure that our results
for domains identified to behave differently within each country are within
a 5\% significance level. We set $p \leq 1-{.05}^{1/n_{dom_{c}}}$, where
$n_{dom_{c}}$ represents the number of domains tested in country $c$.
%
In the absence of significant within-country differences, a statistically
significant difference for a domain would suggest the presence of
a domain-specific characteristic that results in the two resource records
undergoing different censorship mechanisms within the corresponding country.

\parait{Results.}

